Differences from our PPoPP Conference Paper \cite{KBP16}

### 2019-01-25 latex/toms/experiments.tex
changed the size of the synthetic low rank experiments

\begin{figure}
\subfloat[Synthetic Low Rank \label{fig:luclr81}]{
\includegraphics[width=0.45\textwidth, height=2in]{data/plots/luclr81.pdf}
}
\subfloat[Tiny Imagenet \label{fig:lucrw}]{
\includegraphics[width=0.45\textwidth, height=2in]{data/plots/lucrw64.pdf}
}
\caption{LUC comparison of \MU, \HALS, \BPP, \ADMM, \Nestrov\ on 4D Synthetic Low Rank Tensor of size 162x162x162x162 on 81 Titan nodes as 3x3x3x3 Processor Grid on CPU and Realworld TinyImagenet Dataset on 64 Titan nodes as 2x4x2x4 processor grid}
\label{fig:luccomp}
\end{figure}

@@

%%%%%%%%%%%%%%%%%
%Configuration Sweep
%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth, height=2.5in]{data/plots/confsweep4d.pdf}
\caption{Processor Grid sweep of a 162x162x162x162 synthetic low rank tensor on 81 nodes in Titan as 81x1x1x1, 27x3x1x1, 9x3x3x3, 3x3x3x3 grids represented as p=1,2,3,4 respectively. The algorithms alg=0,1,2,4,5 are \MU, \HALS, \BPP, \ADMM, \Nestrov\ respectively.}
\label{fig:confsweep4D}
\end{figure}

>>>>

\begin{figure}
\subfloat[Synthetic Low Rank \label{fig:luclr81}]{
\includegraphics[width=0.45\textwidth, height=2in]{data/plots/luclr81.pdf}
}
\subfloat[Tiny Imagenet \label{fig:lucrw}]{
\includegraphics[width=0.45\textwidth, height=2in]{data/plots/lucrw64.pdf}
}
\caption{LUC comparison of \MU, \HALS, \BPP, \ADMM, \Nestrov\ on 4D Synthetic Low Rank Tensor of size $384 \times 384 \times 384 \times 384$ on 81 Titan nodes as 3x3x3x3 Processor Grid on CPU and Realworld TinyImagenet Dataset on 64 Titan nodes as 2x4x2x4 processor grid}
\label{fig:luccomp}
\end{figure}

@@

%%%%%%%%%%%%%%%%%
%Configuration Sweep
%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth, height=2.5in]{data/plots/confsweep4d.pdf}
\caption{Processor Grid sweep of a $384 \times 384 \times 384 \times 384$ synthetic low rank tensor on 81 nodes in Titan as 81x1x1x1, 27x3x1x1, 9x3x3x3, 3x3x3x3 grids represented as p=1,2,3,4 respectively. The algorithms alg=0,1,2,4,5 are \MU, \HALS, \BPP, \ADMM, \Nestrov\ respectively.}
\label{fig:confsweep4D}
\end{figure}
